\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{import}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{microtype}
\usepackage{lipsum}
\usepackage{helvet}

\name{Noor}{Mohammed B}
\newcommand*{\customcventry}[7][.13em]{
	\begin{tabular}{@{}l}
	{\bfseries #4} \
	{\itshape #3}
	\end{tabular}
	\hfill
	\begin{tabular}{l@{}}
	{\bfseries #5} \
	{\itshape #2}
	\end{tabular}
	\ifx&#7&
	\else{\
	\begin{minipage}{\maincolumnwidth}
	\small#7
	\end{minipage}}\fi
	\par\addvspace{#1}
}

\newcommand*{\customcvproject}[4][.25em]{
	\begin{tabular}{@{}l}
	{\bfseries #2}
	\end{tabular}
	\hfill
	\begin{tabular}{l@{}}
	{\itshape #3}
	\end{tabular}
	\ifx&#4&
	\else{\\
	\begin{minipage}{\maincolumnwidth}
	\small#4
	\end{minipage}}\fi
	\par\addvspace{#1}
}

\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Fullstack Blockchain Developer}\end{center}
\begin{center}
	\begin{tabular}{ c c c }
		\faMobile\enspace +91 9746580702                                                                 &
		\enspace noormohammedb@protonmail.com                                                            &
		\faHome\enspace Dubai, UAE
		\\ \faLinkedin\enspace \color{blue} \href{https://linkedin.com/in/noormohammedb}{in/noormohammedb}&
		\faGithub\enspace \color{blue} \href{https://github.com/noormohammedb}{github.com/noormohammedb} &
		\enspace {$\mathbb{X}$}\enspace \color{blue} \href{https://x.com/0xnoormohammedb}{x.com/0xnoormohammedb}
	\end{tabular}
\end{center}

\section{Summary}
 {I am a passionate blockchain developer with over two years of experience in full-stack development. Recently graduated from the Polkadot Blockchain Academy, I am skilled in building APIs with Actix Web, Tokio, and Axum. I am proficient in Rust with a deep understanding of its ecosystem, coupled with experience in Node.js and TypeScript. Since 2017 I've been an advocate in the blockchain space with a proven track record of winning hackathons with Ethereum blockchain technologies.}

\section{Skills}
 {Rust - TypeScript - React - Golang - Polkadot SDK Substrate - AWS - Tmux - Node.js Express - Nginx - TokioAxum - Git - PM2 - SSH - ActixWeb - VIM - Certbot - IPFS - Linux - DevOps - Docker - GraphQL - Gitlab CI - K8s}

\section{Professional Experience}
\customcventry{06/2022 ‐ present}{{\color{blue}\href{https://gnginfotech.com/}{(GnG Innovations)}}}{Software Developer,}{Dubai, UAE}{}{
	{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
				\item Developed real-time WebSocket chat system using Node.js with Socket.IO for seamless communication.
				\item Designed and implemented backend APIs using Node.js with TypeScript, ensuring efficient data flow and processing.
				\item Developed backend systems in Rust using SQLx for migrations, Tokio for asynchronous programming, and Axum for web APIs. Integrated SMTP for email functionality and managed JSON with serde-json. Implemented JWT for authentication.
				\item Configured NGINX reverse proxy to efficiently route incoming requests to Node.js and Rust backend APIs.
				\item Deployed React Next.js frontend websites and stored assets on AWS S3 buckets for efficient asset management.
				\item Managed Azure cloud infrastructure for deployment, ensuring scalability, availability, and security of applications.
				\item Led team setup efforts by hiring and onboarding new developers, fostering a collaborative and productive work environment.
				\item Collaborated with clients to brainstorm and refine product ideas, translating concepts into functional systems to meet project requirements.
			\end{itemize}}}

\customcventry{08/2022 ‐ 10/2022}{{\color{blue}\href{https://linkdot.xyz/}{(LinkDot.xyz)}}}{Blockchain Developer,}{Banglore, IN}{}{
	{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
				\item Joined LinkDot.xyz as the sole blockchain developer, rearchitected the entire product for maximum decentralization, and implemented ERC721 contracts using Solidity.
				\item Brainstormed with the team to refine product ideas and requirements.
				\item Integrated ERC721 contracts with the Next.js frontend using Ethers.js, ensuring seamless interaction with the blockchain.
			\end{itemize}}}

\customcventry{11/2020 ‐ 04/2021}{\color{blue}(MediSheets)}{Backend Developer,}{Kerala, IN}{}{
	{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
				\item Worked as a Backend Developer at Medisheets, a startup addressing supply chain issues in the pharmaceutical industry.
				\item Built REST endpoints according to specifications with node.js express with postgresql for database and documented them with apiDoc for clarity and accessibility.
				\item Collaborated in a team of 5 developers using GitLab, Jira, Slack, Zoom, etc., for project management and communication.
				\item Set up automated deployment processes with Docker and GitLab CI, streamlining development workflows and ensuring consistency across environments.
			\end{itemize}}}


\customcventry{05/2021 ‐ 05/2022}{{{Freelancer}}}{Application Deployment,}{Kerala , IN}{}{
	{\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
				\item Acquired extensive knowledge of Linux CLI and secure deployment best practices to ensure robust hosting environments.
				\item Provided guidance on optimizing server performance and reliability, utilizing tools like Nginx, PM2, and other relevant technologies to achieve seamless deployment and operation of applications.
				\item Implemented best practices for secure and scalable deployment, including setting up SSH access, configuring firewalls with UFW, implementing intrusion detection with Fail2ban, and managing SSL certificates with Certbot.
				\item Leveraged expertise to assist peers in deploying their applications securely and efficiently on raw Linux servers, including AWS EC2 instances and other VPS providers.
			\end{itemize}}}


\clearpage

\section{Personal Projects}
\begin{itemize}[label=\textbullet]
	\item \textbf{TCP Rust} - Implemented a basic TCP/IP stack from the ground up, focusing on the TCP three-way handshake (SYN, SYN-ACK, ACK), utilizing the tun\_tap interface to create a virtual network interface. The project demonstrates a deep understanding of network protocols and low-level network programming, showcasing proficiency in systems programming and network stack development. \\
	      Project Source Code: \textcolor{blue}{\href{https://github.com/noormohammedb/rust-tcp-implementation/}{\textls[-50] {github.com/noormohammedb/rust-tcp-implementation/}}}

	\item \textbf{Rust Blockchain from scratch UTXO POW} - Developed a proof-of-work blockchain from scratch in Rust, utilizing the UTXO model and `clap` for CLI functionality. Implemented genesis state, coinbase transaction, and block validation. Utilized embedded `sled` database for blockchain data storage. Designed mining process with nonce iteration for block creation. \\
	      Project Source Code: \textcolor{blue}{\href{https://github.com/noormohammedb/blockchain-pow-from-scratch-rust-utxo/}{\textls[-50] {github.com/noormohammedb/blockchain-pow-from-scratch-rust-utxo/}}}


	\item \textbf{Blockchain Simulation in Rust} - Developed a simplified blockchain-like system in Rust for educational purposes. The system includes a basic runtime that manages system-level state and account balances. Implemented functionality for executing blocks of transactions, with each transaction being dispatched to the appropriate module for execution. The project served as a practical exploration of Rust’s capabilities for systems programming and provided a foundational understanding of blockchain technology  \\
	      Project Source Code: \textcolor{blue}{\href{https://github.com/noormohammedb/rust-state-machine/}{\textls[-50] {github.com/noormohammedb/rust-state-machine/}}}

\end{itemize}

\section{ACHIEVEMENTS \& CONTRIBUTIONS}
 {\begin{itemize}[label=\textbullet]
	  \item LFGrow hackathon- Second Prize - \underline{\color{blue}\href{https://ethglobal.com/showcase/zilly-b3y8b}{EthGlobal}}
	        \newline A Global web3 hackathon conducted by EthGlobal Community to
	        build application on top of LENS PROTOCOL which is a
	        decentralised social graph using polygon blockchain.

	  \item Web3hacks hackathon - Second Prize - \underline{\color{blue}\href{https://devfolio.co/projects/whistleblower-c8a5}{devfolio}}
	        \newline Won 2nd prize in a hackathon by developing “WhistleBlower-Dapp”, a Web3
	        alternative to WikiLeaks. The DApp uses Ethereum for metadata storage, IPFS for
	        document storage, and was built with React, Web3.js, Ganache, and Truffle Suite.

	  \item Open Source Contribution - \underline{\color{blue}\href{https://github.com/macvk/dnsleaktest}{dnsleaktest}}
	        \newline Converted "go version"
	        api calls of dnsleaktest cli tool to
	        asynchronous method using goroutine. \underline{\color{blue}\href{https://github.com/macvk/dnsleaktest/pull/12}{Github PR}}

  \end{itemize}}

\section{Education}
\customcventry{2019-2022}
{\color{blue}\href{https://gpckasaragod.ac.in/} {Govt Polytechnic Collage Kasaragod, India}}
{Diploma In Computer Engineering}{Kasaragod, IN}{}{}
{Relevant Courses:
	Data Structures, Algorithms, Operating Systems, Databases, Computer Networks,
	Software Engineering, Assembly Programming, Microprocessor and Interfacing,
	Computer Architecture, etc.}
\newline

\customcventry{2015-2017}{{TIHSS Naimaramoola}}{Hight School Computer Science}{Kasaragod, IN}{}{}{Relevante Courses: Mathematics, Computer Science, Physics, Chemistry  etc.}


% Skills Section is not required because it is already mentioned in the summary section.
% can mention certifications if any

% \section{Skills}
%  {\customcvproject{Programming Languages and Library}{}
%   {\begin{itemize}
% 		  \item Rust, TypeScript, Rust-macros, Node.js JavaScript, Socket.IO , React, Golang
% 	  \end{itemize}
%   }
%  }

%  {\customcvproject{Technical Knowledge}{}
%   {\begin{itemize}
% 		  \item Vim, Tmux, Git, Linux, Docker, AWS, Nginx, Systemd, SSH, Certbot, GraphQL, Gitlab CI
% 	  \end{itemize}
%   }
%  }


\section{Languages}
\begin{multicols}{2}
	\begin{itemize}[label=\textbullet]
		\item \textbf{English} [Fluent]
		\item {\textbf{Hindi} [Basic] - Learning}
		\item {\textbf{Tamil} [Basic]}
		\item {\textbf{Malayalam} [Native]}
	\end{itemize}
\end{multicols}
\end{document}